Local to global N input modelling

### 2025-05-16 08_manuscript/08_manuscript.qmd
Nicer harvest size figure

file.path(output_farm_data_path, "farm_harvest_size.qs") %>% 
  qread() %>% 
  mutate(weight = weight %>% set_units("g") %>% set_units("kg")) %>% 
  select(c(farm_ID, weight)) %>% 
  ggplot(aes(x = weight)) +
  geom_histogram(binwidth = 0.25, colour = "black", fill = "salmon", alpha = 0.5) +
  scale_y_continuous(limits = c(0,500)) +
  labs(y = "Frequency", x = "Harvest weight") +
  theme_classic() +
  theme(legend.position = "none", aspect.ratio = 0.75)
```

>>>>

file.path(output_farm_data_path, "farm_harvest_size.qs") %>% 
  qread() %>% 
  mutate(weight = weight %>% set_units("g") %>% set_units("kg")) %>% 
  select(c(farm_ID, weight)) %>% 
  ggplot(aes(x = weight)) +
  geom_histogram(binwidth = 0.25, colour = "black", fill = "salmon", alpha = 0.75) +
  scale_y_continuous(limits = c(0,500)) +
  labs(y = "Frequency", x = "Harvest weight") +
  theme_classic() +
  theme(
    legend.position = "none", 
    aspect.ratio = 0.75
  )
```
